% !TeX spellcheck = <none>
\chapter*{Acknowledgements}

Many people supported and helped me during the production of this thesis. For this reason I want to thank each of them.
\vspace{0.5cm}

To \textbf{Aris A.}: thank for giving me the possibility to experience a such great opportunitiy, it has been an honor having you as advisor.
\vspace{0.5cm}

To \textbf{Francesco B.}: thank you for giving me the opportunity to do research at ISI Foundation and for trusting me in this project. You have been patient and supportive during all the time. It is difficult to find someone such professional and forthcoming at the same time. I am greatful to had the opportunity of working with you, it made me grow both from human and professional point of view.
\vspace{0.5cm}

To \textbf{Tommaso L.}: thank you for helping me building this project, on every big and little detail. You have been very patient and helpful, and you were always ready to give an hand when I needed. You teached me many things, and without you I would have not been able to do it so exhaustively. 
\vspace{0.5cm}

To \textbf{my parents}: it is thanks to you that I can celebrate this achievement. You gave me the opportunity to follow my passions and my professional carrer, giving me advises and trust in what I believed. There are not many words that can describe how much you did for me in all these years.
\vspace{0.5cm}

To \textbf{my family}: thank you for your support. Your security gives me always the strength to accomplish my objectives.
\vspace{0.5cm}

To \textbf{Ale}: thank you for being my best friend. You have always been at my side, even if it was the wrong one. You supported me, listened to me and gave me advises many many times during more than half of my life now, even during the most difficult times. Thank you for keep doing it every day.
\vspace{0.5cm}

To \textbf{Azzura}: the best roommate. You teached me how the real world works. You always support me and give me strength, without ever forget to laugh. Thank you for taking me under your wing, I will try to give you at least a half of what you gave me.
\vspace{0.5cm}

To \textbf{Asia} and \textbf{Francesca}: thank you for always listening to me and to making me laugh. It is not easy to find friends like you, and I feel lucky to have you.
\vspace{0.5cm}

To \textbf{my friends and teacher at dance classes}: learning to dance with you is the activity I appreciate the most during the day. You make me feel good and carefree when I am with you, and this is what gives me stength to face all the difficulties. A special mention goes to Marianna, my dance partner, that became also my confident.
\vspace{0.5cm}

To \textbf{my collegues at AVI}: you made me discover a good world, one in which only few believes in. Thank you for opening my eyes and teaching me to face life in a bright way. 
\vspace{0.5cm}

To \textbf{Seb}: thank you for supporting and helping me in these months. You have been a safe and happy place for me. It is always a pleasure sharing our knowledge and interests.
 
\begin{flushright}
	Sincerely,\\
	Ilaria
\end{flushright}
